\TheTitle

### 2017-07-14 paper/discussion.tex
fixing capitalization

Contributors making merges need to understand more than just what merges
a commit was collected into before reaching the repository of the
contributor. It is also important to understand order that the related
commits were made, as the order tells the story of what the developer
was thinking as they were writing the changes. The current \mt model
does not order the commits, simply placing them randomly. This is the
primary reason behind this participant's request to use both
simultaneously. \tool is able to help with the aggregation of the
information, and provide a better understanding of the next merge
involved in integrating this commit, but the DAG visualization in gitk
provides the full story of the commit instead of hiding it behind a
layer of abstraction.

@@

While git includes gitk and git log provides a visualization of the DAG
with \verb|git log --graph|, many of the participants in our study were
unfamiliar with the DAG visualizations shown by these tools. Other tools
may provide better summarizations and visualizations, but we are unaware
of any. We investigated the gui tools for Linux on the git
website\footnote{\url{https://git-scm.com/download/gui/linux}}, but none
of the tools, with the exception of Gitk and git log, were able to
produce a visualization of the DAG for the Linux repository.
Investigating the tools more deeply, it appears that GitKraken is the
most popularly cited git client. The visualization provided by GitKraken
was centered around the same DAG metaphor used by git log. GitKraken was
unable to produce a visualization for the Linux repository on our
system. Inspecting these tools on smaller repositories show that the
visualizations of the DAG were very similar to the visualization in
Gitk.

>>>>

Contributors making merges need to understand more than just what merges
a commit was collected into before reaching the repository of the
contributor. It is also important to understand order that the related
commits were made, as the order tells the story of what the developer
was thinking as they were writing the changes. The current \mt model
does not order the commits, simply placing them randomly. This is the
primary reason behind this participant's request to use both
simultaneously. \tool is able to help with the aggregation of the
information, and provide a better understanding of the next merge
involved in integrating this commit, but the DAG visualization in Gitk
provides the full story of the commit instead of hiding it behind a
layer of abstraction.

@@

While git includes Gitk and git log provides a visualization of the DAG
with \verb|git log --graph|, many of the participants in our study were
unfamiliar with the DAG visualizations shown by these tools. Other tools
may provide better summarizations and visualizations, but we are unaware
of any. We investigated the gui tools for Linux on the git
website\footnote{\url{https://git-scm.com/download/gui/linux}}, but none
of the tools, with the exception of Gitk and git log, were able to
produce a visualization of the DAG for the Linux repository.
Investigating the tools more deeply, it appears that GitKraken is the
most popularly cited git client. The visualization provided by GitKraken
was centered around the same DAG metaphor used by git log. GitKraken was
unable to produce a visualization for the Linux repository on our
system. Inspecting these tools on smaller repositories show that the
visualizations of the DAG were very similar to the visualization in
Gitk.

### 2017-07-14 paper/introduction.tex
fixing capitalization

One major challenge with visualizing the arrival of commits to a
repository is that Git does not store the date that a commit was merged
into another branch, including the master branch. To complicate the
problem, the DAG only has references to the parents of a commit (a
model necessary for the operation of Git), but maintainers would prefer
knowing the path a commit followed to reach the master repository.
Tracing a path that any commit followed to the master repository would
imply that for any given commit, we know the next merge in the direction
of the master branch. A user could inspect the commits that arrived into
the master branch within a given time-frame by checking which commits
were merged during that time-frame.

>>>>

One major challenge with visualizing the arrival of commits to a
repository is that git does not store the date that a commit was merged
into another branch, including the master branch. To complicate the
problem, the DAG only has references to the parents of a commit (a
model necessary for the operation of git), but maintainers would prefer
knowing the path a commit followed to reach the master repository.
Tracing a path that any commit followed to the master repository would
imply that for any given commit, we know the next merge in the direction
of the master branch. A user could inspect the commits that arrived into
the master branch within a given time-frame by checking which commits
were merged during that time-frame.

### 2017-07-14 paper/model.tex
fixing capitalization

To illustrate this model we will use a small example: assume the commits
represented in Figure~\ref{fig:repoEvents} show the sequence of events
in a repository. The sequence starts with the initial commit in the
master branch of the master repository at time $t_0$. Repository event 1
is a commit, which gets forked into a separate repository, \textit{Repo
  A}, where another commit is made, event 2. Event 5 is a merge event,
merging event 2, 3, and 4 into \textit{Repo A}. Event 5 is branched
from, commit 6 happens in the new branch, while commit 7 is added
simultaneously to the original branch in \textit{Repo A}. Events 11 and
12 are both merge events, merging changes made in \textit{Repo A} into
the master branch of the master repository. As every repository is a
first-class repository, including local copies and forks, Git does not
distinguish between forked repositories and branches, and in neither
case does it explicitly record where a commit was made. In this case,
commits are performed in various repositories and branches. The DAG
representation of these events is shown in Figure~\ref{fig:repoDAG}.

@@

\begin{algorithm}
        \caption{Computing the \mt of Linux Git's DAG}\label{fig:alg}
        \begin{algorithmic}
                \Function{ComputeMergeTree}{DAG}: tree
                \State {\# Compute the tree from the DAG of Linux repository.}
                \State {\# Returns $Tree$, a graph containing every commit }
                \State {\# in DAG with the path it followed to master.}

>>>>

To illustrate this model we will use a small example: assume the commits
represented in Figure~\ref{fig:repoEvents} show the sequence of events
in a repository. The sequence starts with the initial commit in the
master branch of the master repository at time $t_0$. Repository event 1
is a commit, which gets forked into a separate repository, \textit{Repo
  A}, where another commit is made, event 2. Event 5 is a merge event,
merging event 2, 3, and 4 into \textit{Repo A}. Event 5 is branched
from, commit 6 happens in the new branch, while commit 7 is added
simultaneously to the original branch in \textit{Repo A}. Events 11 and
12 are both merge events, merging changes made in \textit{Repo A} into
the master branch of the master repository. As every repository is a
first-class repository, including local copies and forks, git does not
distinguish between forked repositories and branches, and in neither
case does it explicitly record where a commit was made. In this case,
commits are performed in various repositories and branches. The DAG
representation of these events is shown in Figure~\ref{fig:repoDAG}.

@@

\begin{algorithm}
        \caption{Computing the \mt of Linux from the DAG}\label{fig:alg}
        \begin{algorithmic}
                \Function{ComputeMergeTree}{DAG}: tree
                \State {\# Compute the tree from the DAG of Linux repository.}
                \State {\# Returns $Tree$, a graph containing every commit }
                \State {\# in DAG with the path it followed to master.}

### 2017-07-14 paper/relatedwork.tex
fixing capitalization

Codebook, Hipikat, Fractal Figures, EPOSee, and Evolution Radar all work
with data from CVS repositories. Our goal is to provide information
about Git repositories, specifically the Linux master repository. Fewer
tools are available for generating visualizations and summaries of Git
repositories, potentially due to the DAG model used by Git.

@@

Git itself is shipped with summarization and visualization tools: the
\verb|git log| command and Gitk, which is a graphical tool for the
purpose of browsing the DAG of the repository. Many other tools are
designed with a similar visual metaphore as what is presented in Gitk,
including GitKraken, Github Desktop and web interfaces, the Git Lab web
interface, the Bitbucket web interface, are a few examples. The Gitk
interface is built around the central DAG viewer. The DAG displays the
repository events on their respective branches, the author, and the date
that the event was authored. A user can select an event to view addition
information about it, including the full commit log, the parents and
children of the event, and the diff generated if modifications were
made. In the case of the Linux kernel, merges are not resolved as merge
conflicts in the master repository, but by the developers prior to
merging through rebase operations. With this development model, no
merges will have modified any files, and will not show a diff. While the
merge does not make changes directly, the effects of merging the commits
persist, but Gitk is unable to provide an aggregated view of the files
modified, the patches for those files, and the authors who contributed
commits to that merge.

>>>>

Codebook, Hipikat, Fractal Figures, EPOSee, and Evolution Radar all work
with data from CVS repositories. Our goal is to provide information
about git repositories, specifically the Linux master repository. Fewer
tools are available for generating visualizations and summaries of git
repositories, potentially due to the DAG model used by git.

@@

Git itself is shipped with summarization and visualization tools: the
\verb|git log| command and Gitk, which is a graphical tool for the
purpose of browsing the DAG of the repository. Many other tools are
designed with a similar visual metaphore as what is presented in Gitk,
including GitKraken, Github Desktop and web interfaces, the GitLab web
interface, the Bitbucket web interface, are a few examples. The Gitk
interface is built around the central DAG viewer. The DAG displays the
repository events on their respective branches, the author, and the date
that the event was authored. A user can select an event to view addition
information about it, including the full commit log, the parents and
children of the event, and the diff generated if modifications were
made. In the case of the Linux kernel, merges are not resolved as merge
conflicts in the master repository, but by the developers prior to
merging through rebase operations. With this development model, no
merges will have modified any files, and will not show a diff. While the
merge does not make changes directly, the effects of merging the commits
persist, but Gitk is unable to provide an aggregated view of the files
modified, the patches for those files, and the authors who contributed
commits to that merge.
